Comparative Evaluation of Spark and Flink Stream Processing

### 2017-03-04 paper/paper.tex
[paper] added the introducation of preformance results

\end{abstract}
Recent years have witnessed a big development improvements of Big Data frameworks such as Apache Spark and Apache Flink. For example, both frameworks support real-time
streaming processing. While which platform is the best still an open question. 
In this paper, we provide a performance comparison of streaming data processing in Apache Spark and Apache Flink, by measuring different performance metrics, namely latency and throughput. In addition, we cover some key aspects of streaming data applications and how they are handled in both frameworks. The experiment is done using multiple streaming workloads over real-world datasets.
\section{Introduction}

@@

\par The remainder of this paper is organized as follows.
In Section 2, we present the main characteristics, APIs, and main data abstraction of Apache Spark and Flink. Section 3  presents the general aspects of streaming processing, the design and implementation of experimental workloads. Section 4
provides and compares the performance results of the different workloads. Finally, Section 5 gives the overall conclusion.

@@

\par Apache Spark is an open source project that provide general framework for large-scale data processing \cite{spark}. It offers programming API in Java, Scala, Python and R. Its stack includes set of built-in modules including Spark SQL, MLlib for machine learning, GraphX for graph processing, and Spark Streaming to process real-time data streams. It can access different data sources including Hadoop Distributed File System (HDFS), Apache Cassandra database, Apache HBase database etc.

@@

\par Apache Flink is an open source project that provide large-scale, distributed stream processing platform, while the batch processing treated as special case of streaming applications (i.e., finite stream)  \cite{flink}.
It offers programming API in Java and Scala. Its software stack includes the core DataStream and DataSet APIs with additional libraries such as Complex event processing for Flink (FlinkCEP), Machine Learning for Flink (FlinkML), and Flink Graph API (Gelly).

@@

This section provides and compares the performance results of the different workloads.

>>>>

\end{abstract}
Recent years have witnessed a advances in the  development of Big Data frameworks like Apache Spark and Apache Flink. For example, both frameworks support real-time
streaming processing. While which platform is the best still an open question. 
In this paper, we provide a performance comparison of streaming data processing in Apache Spark and Apache Flink, by measuring different performance metrics, namely latency and throughput. In addition, we cover some key aspects of streaming data applications and how they are handled in both frameworks. The experiment is done using multiple streaming workloads over real-world datasets.
\section{Introduction}

@@

\par The remainder of this paper is organized as follows.
In Section 2, we present the main characteristics, APIs, and main data abstraction of Apache Spark and Flink. Section 3  presents the general aspects of streaming processing, the design and implementation of experimental workloads. Section 4
provides and compares the performance results of the different workloads. Last, Section 5 gives the overall conclusion.

@@

\par Apache Spark is an open source project that provide general framework for large-scale data processing \cite{spark}. It offers programming APIs in Java, Scala, Python and R. Its stack includes set of built-in modules including Spark SQL, MLlib for machine learning, GraphX for graph processing, and Spark Streaming to process real-time data streams. It can access different data sources including Hadoop Distributed File System (HDFS), Apache Cassandra database, Apache HBase database etc.

@@

\par Apache Flink is an open source project that provide large-scale, distributed stream processing platform, while the batch processing treated as special case of streaming applications (i.e., finite stream)  \cite{flink}.
It offers programming APIs in Java and Scala. Its software stack includes the core DataStream and DataSet APIs with additional libraries such as Complex event processing for Flink (FlinkCEP), Machine Learning for Flink (FlinkML), and Flink Graph API (Gelly).

@@

\par This section presents the results of performance evaluation in Spark (2.0.2) and Flink (1.1.3) for the streaming workloads were described in Section 3.2. Specifically, we provide  the measurements of latency and throughput of the benchmarking workloads execution in Spark and Flink. We carried the experiment by setup the Kafka stream as described in Section 3.1 on local machine\footnote{ The experiments have been carried  on single machine with Ubuntu 16.04 LTS os, Intel® Core™ i5-6200U CPU @ 2.30GHz × 4  processor, and 16 GB of memory.  }, and run the different workloads on the same machine (i.e., local mode) to obtain the performance results.

\par We consider the time delay between the streaming time of record in Kafka and the 
finish processing time in a workload as the platform's processing latency (measured in milliseconds). On the other hand, the number of processed stream's records (aircrafts position messages) per second within each streaming workload is the throughput measure. Since the Spark Streaming is micro-batch based,  We examine the effect of different batch intervals
of the Spark Streaming on the performance measurements.
\subsection{Latency Measurements}
\subsection{Throughput Measurements}
